Example bulk RNA-seq analysis 7

### 2024-05-29 dataprep/bulkrna2.Rmd
bulkRNAseq data

---
title: "Example bulk RNA-seq analysis 1"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP128998 and we are comparing the cells grown in normal glucose condition (control) to the high glucose condition (case).

@@

name = "SRP128998"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP128998",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,1,1,1,0,0,0,0,0,0))
samplesheet$VPA <- as.factor(c(0,0,0,1,1,1,0,0,0,1,1,1))
s1 <- subset(samplesheet,VPA==0)

@@

w <- getDEE2("hsapiens", samplesheet$SRR_accession,
  metadata=mdat,legacy = TRUE)

x <- Tx2Gene(w)
x <- x$Tx2Gene

@@

# counts
x1 <- x[,which(colnames(x) %in% s1$SRR_accession)]

@@

saveRDS(m,"bulkrna1.Rds")

>>>>

---
title: "Example bulk RNA-seq analysis 2"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP038101 and we are comparing the cells grown in normal condition (control) to those grown with addition of Azacitidine (case).

@@

name = "SRP038101"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP038101",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,0,0,0))
s1 <- samplesheet

@@

w <- getDEE2("hsapiens",samplesheet$SRR_accession,metadata=mdat,legacy = TRUE)
x <- Tx2Gene(w)
x <- x$Tx2Gene

@@

# counts 
x1 <- x[,which(colnames(x) %in% samplesheet$SRR_accession)]

@@

saveRDS(m,"bulkrna2.Rds")

### 2024-05-29 dataprep/bulkrna3.Rmd
bulkRNAseq data

---
title: "Example bulk RNA-seq analysis 2"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP038101 and we are comparing the cells grown in normal condition (control) to those grown with addition of Azacitidine (case).

@@

name = "SRP038101"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP038101",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,0,0,0))
s1 <- samplesheet

@@

w <- getDEE2("hsapiens",samplesheet$SRR_accession,metadata=mdat,legacy = TRUE)
x <- Tx2Gene(w)
x <- x$Tx2Gene

@@

saveRDS(m,"bulkrna2.Rds")

>>>>

---
title: "Example bulk RNA-seq analysis 3"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP096178 and we are comparing the cells grown in normal condition (control) to those grown with addition of SAHA (case).

@@

name = "SRP037718"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP037718",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]

samplesheet$trt <- as.factor(c(1,1,1,0,0,0))
s1 <- samplesheet

@@

w <- getDEE2("hsapiens",s1$SRR_accession,metadata=mdat,legacy = TRUE)
x <- Tx2Gene(w)
x <- x$Tx2Gene

@@

saveRDS(m,"bulkrna3.Rds")

### 2024-05-29 dataprep/bulkrna4.Rmd
bulkRNAseq data

---
title: "Example bulk RNA-seq analysis 2"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP038101 and we are comparing the cells grown in normal condition (control) to those grown with addition of Azacitidine (case).

@@

name = "SRP038101"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP038101",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,0,0,0))
s1 <- samplesheet

@@

saveRDS(m,"bulkrna2.Rds")

>>>>

---
title: "Example bulk RNA-seq analysis 4"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP038101 and we are comparing the cells expressing a set7kd shRNA construct (case) compared to the scrambled construct (control).

@@

name = "SRP096177"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP096177",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,0,0,0))
s1 <- samplesheet

@@

saveRDS(m,"bulkrna4.Rds")

### 2024-05-29 dataprep/bulkrna5.Rmd
bulkRNAseq data

---
title: "Example bulk RNA-seq analysis 1"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP128998 and we are comparing the cells grown in normal glucose condition (control) to the high glucose condition (case).

@@

name = "SRP128998"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP128998",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,1,1,1,0,0,0,0,0,0))
samplesheet$VPA <- as.factor(c(0,0,0,1,1,1,0,0,0,1,1,1))
s1 <- subset(samplesheet,VPA==0)

@@

saveRDS(m,"bulkrna1.Rds")

>>>>

---
title: "Example bulk RNA-seq analysis 5"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP097759 and we are comparing the effect of control construct versus SAHH overexpression construct.

@@

name = "SRP097759"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP097759",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(0,0,1,1))
s1 <- samplesheet

@@

saveRDS(m,"bulkrna5.Rds")

### 2024-05-29 dataprep/bulkrna6.Rmd
bulkRNAseq data

---
title: "Example bulk RNA-seq analysis 4"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP038101 and we are comparing the cells expressing a set7kd shRNA construct (case) compared to the scrambled construct (control).

@@

name = "SRP096177"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP096177",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
samplesheet$trt <- as.factor(c(1,1,1,0,0,0))
s1 <- samplesheet

@@

saveRDS(m,"bulkrna4.Rds")

>>>>

---
title: "Example bulk RNA-seq analysis 6"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP253951 and we are comparing A549 cells with and without infection with SARS-CoV-2.

@@

name = "SRP253951"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP253951",mdat$SRP_accession),]

samplesheet <- mdat[which(mdat$SRX_accession %in% c("SRX8089264","SRX8089265","SRX8089266","SRX8089267","SRX8089268","SRX8089269")),]

samplesheet$trt <- factor(c(0,0,0,1,1,1))
s1 <- samplesheet

@@

saveRDS(m,"bulkrna6.Rds")

### 2024-05-29 dataprep/bulkrna7.Rmd
bulkRNAseq data

---
title: "Example bulk RNA-seq analysis 6"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP253951 and we are comparing A549 cells with and without infection with SARS-CoV-2.

@@

name = "SRP253951"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP253951",mdat$SRP_accession),]

samplesheet <- mdat[which(mdat$SRX_accession %in% c("SRX8089264","SRX8089265","SRX8089266","SRX8089267","SRX8089268","SRX8089269")),]

samplesheet$trt <- factor(c(0,0,0,1,1,1))
s1 <- samplesheet

@@

w <- getDEE2("hsapiens",samplesheet$SRR_accession,metadata=mdat,legacy = TRUE)
x <- Tx2Gene(w)
x <- x$Tx2Gene

@@

saveRDS(m,"bulkrna6.Rds")

>>>>

---
title: "Example bulk RNA-seq analysis 7"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

The dataset being used is SRP068733 and we are comparing the healthy endothelial cells with a scrambled siRNA to cells treated with a p300 targeting siRNA.

@@

name = "SRP068733"
mdat <- getDEE2Metadata("hsapiens")
samplesheet <- mdat[grep("SRP068733",mdat$SRP_accession),]
samplesheet <- samplesheet[order(samplesheet$SRR_accession),]
SRRvec <- c("SRR3112216","SRR3112217","SRR3112218","SRR3112219","SRR3112220","SRR3112221")
samplesheet <- samplesheet[which(samplesheet$SRR_accession %in% SRRvec),]
samplesheet$trt <- as.factor(c(0,0,0,1,1,1)) 
s1 <- samplesheet

@@

w <- getDEE2("hsapiens",SRRvec,metadata=mdat,legacy = TRUE)
x <- Tx2Gene(w)
x <- x$Tx2Gene

@@

saveRDS(m,"bulkrna7.Rds")
